Optimal (Multiway) Spatial Joins

### 2024-05-30 msj.tex
yufei

It remains to show that we will not map two distinct rectangle $r_1^*, r_2^*\in \bigcup_{i = 1}^{k-2}R_i^*$ to the same tuple $\bm{t}\in \J(R_1',...,R_{k-2}')$. Suppose to the contrary that $r_1^*, r_2^*$ are mapped to the same tuple $\bm{t}$. Let $r_1^*, r_2^*$ be the top-sliced rectangles of $r_1'$ and $r_2'$ respectively. Since $r_1^*$ and $r_2^*$ are disinct, $r_1'$ is not the same as $r_2'$. By our mapping, $\gbot(B_{\bm{t}})$ is $r_1'$ and $r_2'$. Since $\gbot(B_{\bm{t}})$ is unique for each tuple $\bm{t}$, we have a contradiction. Therefore, each rectangle $r^*\in \bigcup_{i = 1}^{k-2}R_i^*$ is mapped to a unique tuple $\bm{t}\in \J(R_1',...,R_{k-2}')$.

\input{4.3.tex}

>>>>

It remains to show that no two distinct rectangles $r_1^*, r_2^* \in \bigcup_{i = 1}^{k-2}R_i^*$ can be mapped to the same tuple in $\J(R_1',...,R_{k-2}')$. Assume, on the contrary, that $r_1^*$ and $r_2^*$ are mapped to the same tuple $\bm{t}\in \J(R_1',...,R_{k-2}')$. Suppose that $r_1^*$ (resp., $r_2^*$) is the top-sliced rectangle of $r_1'$ (resp., $r_2'$). Under our mapping, it must be true that  $r_1' = r_2' = \gbot(B_{\bm{t}})$. However, the distinctness of $r_1^*$ and $r_2^*$ requires $r_1' \ne r_2'$, thus giving a contradiction.

%\input{4.3.tex}
